Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Revision.

>>>>

\paragraph{Manually Extended Embeddings}
From the analysis of Section ~\ref{sec:confm} and also the results in Section ~\ref{sec:modelcomp}, we see that because of the erasure of capitalization information of words, the RNN model is bad at distinguishing between NN and NNP. So we think we can manually extend the embeddings of words by some human made features like capitalized or not, or perhaps even suffix information. This, in our view, will likely improve the performance of the model a lot.
